---
title: "FIRe"
author: 
date: 
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, message = FALSE, warning = FALSE)
```

```{r load_packages}
#Read in required libraries
library("devtools")
library("ggplot2")
library("segmented")
library("plotrix")
library("gridExtra")
library("lubridate")
library("chron")
library("plyr")
library("dplyr")
library("tidyr")
library("tidyverse")
library("broom")
library("ggpubr")
library("minpack.lm")
library("ggpmisc")

library("purrr")
library("magrittr")
library("hms")
library("stringr")
library("forcats")
library("data.table")
library("car")

library("RColorBrewer")
library("cowplot")
library("grid")


```

## Eilat photophysiology
options(scipen = 999)
fire.data<- read_csv("/Users/talimass/Documents/Documents - MacBook Pro/GitHub/Ocullina_Translocation/Ranalysis/data/Annotated FIRe data.csv") ## you need to path this to your data file

#FIRe Data

fire.data$depth <- as_factor(fire.data$depth)
fire_data <- fire.data %>% na.omit()

# fvfm

quartiles <- quantile(fire_data$fv_fm, probs = c(.25,.75))
IQR_cor <- IQR(fire_data$fv_fm)

lower <- quartiles[1] - 1.5*IQR_cor
upper <- quartiles[2] + 1.5*IQR_cor

fvfm_no_outlier <- subset(fire_data, fire_data$fv_fm >lower & fire_data$fv_fm< upper)


fvfm <- ggplot(data = fvfm_no_outlier,aes(x= depth, y=fv_fm, fill= Species))+
  geom_boxplot() + theme_classic() + stat_boxplot(geom = 'errorbar', width = 0.75, position = "dodge") +
  labs(title="Quantum yield of photochemistry in PSII", y="Fv’/Fm’") +
  theme(legend.position = "none") +
  theme(axis.title.y = element_blank()) +
  scale_x_discrete(limits = rev) +
  coord_flip() 

fvfm

### sigma

quartiles <- quantile(fire_data$Sigma, probs = c(.25,.75))
IQR_cor <- IQR(fire_data$Sigma)

lower <- quartiles[1] - 1.5*IQR_cor
upper <- quartiles[2] + 1.5*IQR_cor

sigma_no_outlier <- subset(fire_data, fire_data$Sigma >lower & fire_data$Sigma< upper)


sigma <- ggplot(data = sigma_no_outlier,aes(x= depth, y=Sigma, fill= Species))+
  geom_boxplot() + theme_classic() + stat_boxplot(geom = 'errorbar', width = 0.75, position = "dodge") +
  labs(title="Functional absorption cross-section of PSII", y= "σPSII’(A2)") +
  theme(legend.position = "none") +
  theme(axis.title.y = element_blank()) +
  scale_x_discrete(limits = rev) +
  coord_flip() 
sigma

#### pmax

quartiles <- quantile(fire_data$Pmax.e.s, probs = c(.25,.75))
IQR_cor <- IQR(fire_data$Pmax.e.s)

lower <- quartiles[1] - 1.5*IQR_cor
upper <- quartiles[2] + 1.5*IQR_cor

Pmax.e.s_no_outlier <- subset(fire_data, fire_data$Pmax.e.s >lower & fire_data$Pmax.e.s< upper)

pmax <- ggplot(data = Pmax.e.s_no_outlier,aes(x= depth, y=Pmax.e.s, fill= Species))+
  geom_boxplot() + theme_classic() + stat_boxplot(geom = 'errorbar', width = 0.75, position = "dodge") +
  labs(title="Maximum photosynthetic rate ", y="Pmax (electron s-1 PSII-1)") +
  theme(legend.position = "none") +
  theme(axis.title.y = element_blank()) +
  scale_x_discrete(limits = rev) +
  coord_flip()  
pmax

#### p

quartiles <- quantile(fire_data$p, probs = c(.25,.75))
IQR_cor <- IQR(fire_data$p)

lower <- quartiles[1] - 1.5*IQR_cor
upper <- quartiles[2] + 1.5*IQR_cor

p_no_outlier <- subset(fire_data, fire_data$p >lower & fire_data$p< upper)

p <- ggplot(data = p_no_outlier,aes(x= depth, y=p, fill= Species)) +
  geom_boxplot() +  theme_classic() + stat_boxplot(geom = 'errorbar', width = 0.75, position = "dodge") +
  labs(title="connectivity parameter ", y="p") +
  theme(legend.position = "none") +
  theme(axis.title.y = element_blank()) + 
  scale_x_discrete(limits = rev) +
  coord_flip()
p

ggarrange(fvfm, sigma, pmax, p)

